### 2013-04-18 doc/final_report/report.tex
Finished title page added wordcount etc

Thanks to the users who tested Partridge once it was made generally available
and for their feedback in the form of bug reports and suggestions.

@@

>>>>

Thanks to the users who tested Partridge once it was made generally available
and for their feedback in the form of bug reports and suggestions. Especially
my close friends Alexander Brown and Douglas Eggleton who provided a great deal
of feedback throughout the project. I would also like to thank Matt Pugh for
helping me decide on the name of the project.

@@

\begin{center}
\line(1,0){250}
\end{center}

The image on the front cover is an illustration of a Partridge, donated to the
public domain by Pearson Scott Foresman in 2007. A list of their donations can
be found at
\url{http://commons.wikimedia.org/wiki/Commons:Pearson_Scott_Foresman}
